\documentclass{aastex62}

\usepackage{graphicx}
\usepackage{gensymb}
\usepackage{bm}
\usepackage{amsmath}

\newcommand{\Gus}[1]{\textcolor{red}{#1}}

\newcommand{\Msun}{\ensuremath{\text{M}_\odot}}
\newcommand{\pc}{\ensuremath{\text{pc}}}
\newcommand{\kpc}{\ensuremath{\text{kpc}}}
\newcommand{\Mpc}{\ensuremath{\text{Mpc}}}
\newcommand{\Myr}{\ensuremath{\text{Myr}}}
\newcommand{\Gyr}{\ensuremath{\text{Gyr}}}
\newcommand{\SFR}{\ensuremath{\text{SFR}}}

\newcommand{\GHz}{\ensuremath{\text{GHz}}}

\newcommand{\CI}{\ensuremath{\text{C~\textsc{i}}}}
\newcommand{\CII}{\ensuremath{\text{C~\textsc{ii}}}}
\newcommand{\OIII}{\ensuremath{\text{O~\textsc{iii}}}}
\newcommand{\CO}{\ensuremath{\text{CO}}}

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\uth}{\textsuperscript{th}}
\newcommand{\n}{\text{n}}

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

\newcommand{\mynu}[2]{\ensuremath{\nu_{#1,\text{#2}}}}
\newcommand{\denps}{\ensuremath{P_{\delta,\delta}}}
\newcommand{\xps}[2]{\ensuremath{P_{#1,#2}}}
\newcommand{\pstot}[1]{\ensuremath{P_{#1,\text{tot}}}}
\newcommand{\Bsum}{\ensuremath{\tilde{B}}}

\newcommand{\E}[1]{\mathrm{E}[#1]}
\newcommand{\Var}[1]{\mathrm{Var}[#1]}
\newcommand{\Cov}[2]{\mathrm{Cov}[#1,#2]}
\newcommand{\avg}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\SN}{\ensuremath{\text{S}/\text{N}}}

\newcommand{\penn}{Department of Physics \& Astronomy, University of
Pennsylvania, 209 South 33rd St., Philadelphia, PA 19104, USA}

\begin{document}

\title{CO Interlopers Eloping from [C~\textsc{ii}] Surveys}

\email{abeane@sas.upenn.edu}

\author{Angus Beane}
\affil{\penn}

\author{Adam Lidz}
\affil{\penn}

\author{others}

\begin{abstract}
Intensity mapping stands to be a promising probe of the large-scale structure
of the universe at high redshift ($z>3$). The experiment TIME, currently
undergoing a preliminary engineering run, will measure [\CII] emission from
the redshift ranges $5<z<9$ {\bf check}. An important problem to overcome will
be to remove interloping CO lines. These are lines that are emitted at a
different frequency than [\CII] but are observed at the same frequency from
gas residing at a different redshift. The measurement of [\CII] will be
impacted by emission from three CO transitions
\end{abstract}

\section{Introduction}\label{sec:intro}
At high redshift ($z>3$) the most promising probe of the large-scale structure
(LSS) of the universe is line intensity mapping. Rather than attempting to
resolve individual galaxies, intensity mapping aims to measure the total
emission from an atomic or molecular line of all galaxies within a rather
coarse pixel. Commonly proposed lines include H$\alpha$, H$\beta$, Ly$\alpha$,
[\CII], [\OIII], and 21~cm. During the Epoch of Reionization (EoR;
$z\gtrsim6$), the hydrogen lines also measure the bulk emission from neutral
hydrogen residing in the diffuse intergalactic medium (IGM).

\section{Multi-field Approach}\label{sec:theory}
We describe the multi-field approach in full generality and state some
results. First, we assume a measurement of each of $\xps{i}{j}$. The relevant
variance and covariances are \citep[e.g.][]{2015JCAP...03..034V}
\beq\label{eq:var_cov}
\begin{split}
\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
\xps{i}{j}\xps{i}{k}\text{.}
\end{split}
\eeq
We are then making a measurement of each of $\xps{i}{j}$, $\xps{j}{k}$,
and $\xps{k}{i}$. We model each of these power spectra as
\beq
\xps{i}{j}(k) = B_i(k) B_j(k) \denps(k)\text{.}
\eeq
That is, we are only working in the regime where $r_{i,j}=1$. What this
translates to is that we may only perform this interloper removal on
sufficiently large scales, i.e. where $k<k_{\text{max}}$, where
$k_{\text{max}}$ is set by wherever the lines $i$ and $j$ start to
decorrelate. The value of $k_{\text{max}}$ is the only aspect of our analysis
that is model dependent. Only considering modes up to a $k_{\text{max}}$ is
analogous to a similar procedure in galaxy surveys where only large-scale
information up to a $k_{\text{max}}$ where linear theory is applicable is used.

The Fisher matrix for our measurement is
\beq\label{eq:fisher}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq
where $l$, $l'$, $m$, and $m'$ sum over all lines being considered. Note that
we can make the substitution
\begin{equation*}
\sum_{\substack{l,l'\\l > l'}} \rightarrow 
\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{,}
\end{equation*}
without changing the value of the Fisher matrix. Thus it will sometimes be
easier to compute
\beq\label{eq:fisher4}
F_{i,j} = 
\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{.}
\eeq
We also note that a perfect auto-spectrum measurement will have a limit to the
precision of a $B_i$ as
\beq\label{eq:Bi_auto_snr}
\text{S}/\text{N}(B_i) = \frac{B_i^2}{\sqrt{N_i}}\sqrt{V_k}\text{.}
\eeq
This will be useful to compare to the $\text{S}/\text{N}$ we will compute for
the multi-field approach.

\subsection{Noise-limited Regime} \label{ssec:noise_limited}
We consider the noise-limited regime. In this case, we assume that $N_i \gg
P_i$, so that Equation~\ref{eq:var_cov} reduces to
\beq \label{eq:var_cov_noise}
\begin{split}
\Var{\xps{i}{j}} &= N_iN_j \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= 0 \text{.}
\end{split}
\eeq
We will also assume a white noise spectrum, so that each $N_i$ is a constant
value. In this case, the computation of the Fisher matrix is quite simple. In
fact, we can rewrite it as
\beq\label{eq:fisher_noisedom}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Var{\hat{P}_{l,l'}(k)}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_j}\text{.}
\eeq
For a diagonal element, we can see that we will only get terms when $l=i$ or $l'=i$. Therefore
\beq\label{eq:fisher_noisedom2}
F_{i,i} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l\neq i}}
\frac{B_l^2}{N_iN_l}\denps(k)^2\text{.}
\eeq
Since we are assuming a white noise power spectrum, if we define
\begin{equation*}
V_k \equiv \int \frac{\text{d}k\,k^2}{2\pi^2} \denps(k)^2 V_{\text{surv}}\text{,}
\end{equation*}
then we can simplify Equation~\ref{eq:fisher_noisedom2} to
\beq\label{eq:fisher_noisedom_diag}
F_{i,i} = 
V_k
\sum_{\substack{l\neq i}}
\frac{B_l^2}{N_iN_l}\text{.}
\eeq
For the off-diagonal case, we can see that the only term that will contribute
is when $l=i$ and $l'=j$, or vice-versa. Therefore, we have that
\beq\label{eq:fisher_noisedom_offdiag}
F_{i,j} = V_k
\frac{B_iB_j}{N_iN_j}\text{.}
\eeq
Note that as the number of fields increases, the diagonal elements become much
larger than the off-diagonal elements, assuming the magnitudes of all the
$B_i$'s and $N_i$'s are roughly similar. Therefore, the Fisher matrix becomes
approximately diagonal, as does the covariance matrix, and the errors on the
$B_i$'s become uncorrelated. This matches our naive expectation that
considering additional fields should reduce the degeneracies between each
$B_i$.

Consider the extremely trivial case such that $B_i = B$ and $N_i = N$ for all
lines $i$. In this case, if we have $n_l$ lines, the Fisher matrix reduces to
\beq\label{eq:fisher_supertrivial}
        F_{i,j} = V_k \frac{B^2}{N^2} \times
        \begin{cases}
             n_l-1 & \text{if $i=j$} \\
             1 &\text{if $i\neq j$} \\
        \end{cases}\text{.}
\eeq
In the large $n_l$ limit, the Fisher matrix becomes diagonal, and we can
therefore write the covariance matrix as
\beq\label{eq:cov_supertrivial_largen}
C_{i,j} = \frac{N^2}{V_k B^2} \frac{1}{n_l-1} \delta_{ij}\text{,}
\eeq
where $\delta_{ij}$ is the Kronecker delta. This leads us to the conclusion
that in the noise-dominated regime where each line has comparable
$\text{S}/\text{N}$, the constraining power on each line $i$ scales as
$1/n_l$. In other words, one can improve the constraint on $B_i$ without
executing additional observations of line $i$.

\Gus{Inverting}

In the case of three fields labeled $1$, $2$, and $3$, we can explicitly write
down the Fisher matrix as
\beq
F = V_k
\begin{pmatrix}
\frac{B_2^2}{N_1N_2}+\frac{B_3^2}{N_1N_3} & \frac{B_1B_2}{N_1N_2} & \frac{B_1B_3}{N_1N_3} \\
\frac{B_2B_1}{N_2N_1} & \frac{B_3^2}{N_2N_3}+\frac{B_1^2}{N_2N_1} & \frac{B_2B_3}{N_2N_3} \\
\frac{B_3B_1}{N_3N_1} & \frac{B_3B_2}{N_3N_2} & \frac{B_1^2}{N_3N_1}+\frac{B_2^2}{N_3N_2}\text{.}
\end{pmatrix}
\eeq



\section{CO Measurements} \label{sec:co_measurements}
\subsection{CO Modelling} \label{ssec:co_modelling}
To model the statistical fluctuation and amplitude of the \CO{} intensity maps
we follow \citet{2016ApJ...825..143L}, and briefly summarize the procedure
here. We begin by assuming a Schechter form for the star formation rate
function,
\beq\label{eq:schechter}
\phi(\SFR)\,\text{d}\SFR = \phi_*
\left(\frac{\SFR}{\SFR_*}\right)^{\alpha}\exp{\left[-\frac{\SFR}{\SFR_*}\right]}
\frac{\text{d}\SFR}{\SFR_*}
\eeq
where $\alpha$ is the faint-end slope, $\SFR_*$ is the characteristic
star-formation rate, and $\phi_*$ is the characteristic number density. The
average specific intensity in a line $l$ can be related to the comoving
emissivity by \citep{2011ApJ...741...70L, 2013ApJ...768...15P},
\beq\label{eq:emiss_to_int}
\avg{I_l} = \frac{\epsilon_l}{4\pi \nu_{\text{rest},l}}\frac{c}{H(z)}\text{,}
\eeq
where $\nu_{\text{rest},l}$ is the rest-frame emission frequency and
$\epsilon_l$ is the comoving emissivity, each of line $l$. Assuming a linear
luminosity-SFR relation with a constant of proportionality of $L_0^l$, along
with the Schechter form for the SFR function (Equation~\ref{eq:schechter}), it
follows that \citep{2013ApJ...768...15P},
\beq\label{eq:com_emiss}
\epsilon_l = \phi_* L_0^{l}
\frac{\SFR_*}{1\,\Msun\text{yr}^{-1}}\Gamma{(2+\alpha)}\text{.}
\eeq
We adopt the value of $L_0^{\CO}$ for each line transition from
\citet{2010JCAP...11..016V}.

\subsection{Something} \label{ssec:co_}
We now consider the prospects of measuring the \CO{} transition using a
multi-field approach. First, we choose to label each line with the upper
transitional level, e.g. CO(3-2) is referred to as ``3.'' The relevant Fisher
matrix is then,
\beq\label{eq:co_fisher}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq
where $i$ and $j$ each refer to a line by its upper transitional level and the
$l$, $l'$, $m$ and $m'$ sum over all lines considered.

Ignoring interlopers and foreground contamination for a moment, we can
simplify this expression as (see Appendix~\ref{app:fisher_deriv} for a
derivation):
\beq\label{eq:fisher_nocontam}
\begin{split}
F_{i,j} =&
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} \denps^2(k) \\
\times & \left[ 
\delta_{ij} \left( 
\sum_{l\neq i} \frac{B_l^2}{\xps{i}{l}^2 + \pstot{i}\pstot{l}}
+ \frac{1}{\pstot{i}\xps{\delta}{\delta} + \xps{i}{\delta}^2}
\right) \right. \\
&\left. + (1-\delta_{ij}) \left( 
\sum_{l\neq i,j} \frac{B_l^2}{\pstot{l}\xps{i}{j} + \xps{i}{l}\xps{l}{j}}
+\frac{B_i}{\pstot{i}\xps{j}{\delta} + \xps{i}{\delta}\xps{i}{j}}
+ \frac{B_j}{\pstot{j}\xps{i}{\delta} + \xps{j}{\delta}\xps{i}{j}}
+ \frac{B_iB_j}{\xps{i}{j}^2 + \pstot{i}\pstot{j}}
\right)
\right]\text{.}
\end{split}
\eeq
Including the auto-spectra in this analysis simply requires summing over all
$l$ values, replacing $\xps{i}{i}$ with $\pstot{i}$ \Gus{I think this is
correct?}.

\appendix

\section{Fisher Matrix Derivation}\label{app:fisher_deriv}
We show a derivation of Equation~\ref{eq:fisher_nocontam}. First, consider the
Fisher matrix from Equation~\ref{eq:co_fisher}.
\beq\label{eq:co_fisher_2}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq
where $i$ and $j$ each refer to a line by its upper transitional level and the
$l$, $l'$, $m$ and $m'$ sum over all lines considered. We exploit the fact
that the Fisher matrix is unchanged under the substitution,
\begin{equation*}
\sum_{\substack{l,l'\\l > l'}} \rightarrow 
\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{.}
\end{equation*}
Next, we can write down the derivatives of the power spectra as,
\beq\label{eq:psderiv}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
= \left( B_{l'} \delta_{il} + B_l\delta_{il'} \right) \denps(k)\text{.}
\eeq
Now we can also write down the covariance formula as,
\beq\label{eq:cov}
\begin{aligned}
\left(\Cov{\hat{P}_{l,l'}}{\hat{P}_{m,m'}}\right)^{-1} = 
&(\pstot{l}\xps{l'}{m'} + \xps{l}{l'}\xps{l}{m'})^{-1} &&\times \delta_{lm} (1-\delta_{l'm'}) \\
&+ (\pstot{l}\xps{l'}{m} + \xps{l'}{l}\xps{l}{m})^{-1} &&\times \delta_{lm'} (1-\delta_{l'm}) \\
&+ (\pstot{l'}\xps{l}{m'} + \xps{l'}{l}\xps{l'}{m'})^{-1} &&\times \delta_{l'm} (1-\delta_{lm'}) \\
&+ (\pstot{l'}\xps{l}{m} + \xps{l'}{l}\xps{l'}{m})^{-1} &&\times \delta_{l'm'} (1-\delta_{lm}) \\
&+ (\xps{l}{l'}^2 + \pstot{l}\pstot{l'})^{-1} &&\times \delta_{lm} \delta_{l'm'} \\
&+ (\xps{l}{l'}^2 + \pstot{l}\pstot{l'})^{-1} &&\times \delta_{lm'} \delta_{l'm}\text{.}
\end{aligned}
\eeq
We are at liberty to distribute the inverse to all terms since upon inspection
of the Kronecker delta's one and only one term will contribute to the sum. In
the case that the covariance vanishes (e.g.
$\Cov{\hat{P}_{1,2}}{\hat{P}_{3,4}}=0$) we exclude this term from the sum in
Equation~\ref{eq:co_fisher_2}. Since the product,
\begin{equation*}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
% \frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}
\end{equation*}
is symmetric under $(l,l',m,m') \rightarrow (l',l,m',m)$\footnote{and the
summation is as well}, we can equivalently use the following formula for the
covariance:
\beq\label{eq:cov_simple}
\begin{aligned}
\left(\Cov{\hat{P}_{l,l'}}{\hat{P}_{m,m'}}\right)^{-1} = 
&4 (\pstot{l}\xps{l'}{m'} + \xps{l}{l'}\xps{l}{m'})^{-1} &&\times \delta_{lm} (1-\delta_{l'm'}) \\
&+ 2(\xps{l}{l'}^2 + \pstot{l}\pstot{l'})^{-1} &&\times \delta_{lm} \delta_{l'm'}\text{.}
\end{aligned}
\eeq
Combining these facts we can arrive at the following formula for the Fisher matrix:
\beq\label{eq:co_fisher_explicity}
\begin{split}
F_{i,j} = 
\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\denps(k)^2
\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
&\left( B_{l'} \delta_{il} + B_l\delta_{il'} \right)
\left( B_{m'} \delta_{jm} + B_m\delta_{jm'} \right) \\
\times&\left( \frac{4}{\pstot{l}\xps{l'}{m'} + \xps{l}{l'}\xps{l}{m'}} \delta_{lm} (1-\delta_{l'm'})
+ \frac{2}{\xps{l}{l'}^2 + \pstot{l}\pstot{l'}} \delta_{lm} \delta_{l'm'}\right)
\text{.}
\end{split}
\eeq
This formula can be expanded and simplified to give Equation~\ref{eq:fisher_nocontam}.

\bibliography{references}

\end{document}
